Category-Pivot Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection

### 2016-10-01 paper/lncsFormat.tex
paragraph before definition in Introduction section

>>>>

After processing each time window's data, the words in microblogs can be enriched semantically with knowledge base.
In this way, the transfer learning model provides richer semantics and less noise for microblog stream, which promotes the accuracy of event detection significantly. 
The following definitions are the concepts used by the transfer learning model \textsc{TransDetector}.
